Backpropagating Gravitational wave events \kb{can we come up with something a bit more flashy?}

### 2022-05-25 src/tex/ms.tex
Minor abstract wording change.

\begin{abstract}
One promising way to extract information about stellar astrophysics from
gravitational wave catalogs is to compare the catalog to the outputs of
population synthesis modeling with varying physical assumptions.  The parameter
space of physical assumptions in population synthesis is high-dimensional and
the choice of parameters that best represents the evolution of a binary system
may depend on an as-yet-to-be-determined way on the system's properties. Indeed,
measuring the variation of population synthesis parameter settings with binary
properties is one of the principal ways to extract information about binary evolution
astrophysics from catalogs. Here we propose an inference pipeline to
simultaneously infer zero-age main sequence properties and population 
synthesis parameter settings controlling modeled binary
evolution from individual gravitational wave observations of merging compact
binaries.  Our pipeline can efficiently explore the high-dimensional space of
population synthesis settings and progenitor system properties for each system
in a catalog of gravitational wave observations.  We apply our pipeline to
observations in the third LIGO Virgo Kagra Gravitational Wave Transient Catalog.  
We showcase the effectiveness of this pipeline with a detailed study
of the progenitor properties and population synthesis settings that produce
mergers like the observed GW150914.
\end{abstract}

>>>>

\begin{abstract}
One promising way to extract information about stellar astrophysics from
gravitational wave catalogs is to compare the catalog to the outputs of stellar
population synthesis modeling with varying physical assumptions.  The parameter
space of physical assumptions in population synthesis is high-dimensional and
the choice of parameters that best represents the evolution of a binary system
may depend on an as-yet-to-be-determined way on the system's properties. Indeed,
measuring the variation of population synthesis parameter settings with binary
properties is one of the principal ways to extract information about binary
evolution astrophysics from catalogs. Here we propose an inference pipeline to
simultaneously infer zero-age main sequence properties and population synthesis
parameter settings controlling modeled binary evolution from individual
gravitational wave observations of merging compact binaries.  Our pipeline can
efficiently explore the high-dimensional space of population synthesis settings
and progenitor system properties for each system in a catalog of gravitational
wave observations.  We apply our pipeline to observations in the third LIGO
Virgo Kagra Gravitational Wave Transient Catalog.  
We showcase the effectiveness of this pipeline with a detailed study
of the progenitor properties and population synthesis settings that produce
mergers like the observed GW150914.
\end{abstract}
